Convolutional Neural Nets for the MNIST Digit Dataset

### 2014-12-12 tex/paper.tex
Added another image to paper
Formatting is a pain
Add pooling section

@@

>>>>

\begin{figure*}
  \includegraphics[width=\textwidth,height=8cm]{convtrans}
  \caption{This is a tiger.}
  \label{fig:convtrans}
\end{figure*}

@@

The pooling layer reduces the dimension of its input by a factor of n. During forward propagation, each 
unit in the pooling layer looks at an n x n window and applies some pooling operator, either max or mean. 
Though these n x n windows could in principle overlap, in our implementation they do not. No learning occurs 
in this layer, thus backpropagation only serves to directly forward the errors to the previous layer. 
If the pooling layer did max-pooling, then each pooling unit propagates the error to the input unit that 
had the max value with all other errors in that window being zero. If the pooling layer did mean-pooling, 
then each pooling unit propagates the value of the error divided by the number of input units is passed to all input units.
